---
title: "Untitled"
output:
  html_document:
    df_print: paged
---

**Go back to the [main :leftwards_arrow_with_hook: ](https://github.com/ricardohuapaya/Portafolio/blob/main/README.md)** 

**Check the code:**

- [:arrow_forward: Exploratory.R ](https://github.com/ricardohuapaya/Portafolio/blob/main/Projects/chipotl_locations/exploratory_analysis.R)


```{r setup, include=FALSE}
#packages we will use
library(leaflet)
library(leaflet.extras)
library(tidyverse)
library(sf)
library(tidycensus) 
library(tripack)
library(htmlwidgets)
chipotle <- read_csv("datasets/chipotle.csv")
```

## Objetive
Since this is a guided project the main objective is to understand each line of code and comprehend how will it work under future projects. Thanks to DataCamp we have access to our input file `chipotle.csv` which contains all data regarding open and close chipotle around the world, for this case we'll be focusing on the state of South Dakota.

## Data Clean
For this specific project there not much data cleaning to do, after all we are going to be focusing on the open chipotles, for this reason we are only going to filter this variables.

```{r chipotle, echo=TRUE}
closed_chipotle <- 
  chipotle %>%
  filter(closed == TRUE)

chipotle_open <-
  chipotle %>% 
  filter(closed == FALSE) %>% 
  select(-closed)
```


```{r pressure, echo=FALSE}
chipotle_heatmap <- 
  chipotle_open %>% 
  leaflet() %>% 
  addProviderTiles(provider = 'CartoDB') %>%
  addHeatmap(radius =10)


chipotle_heatmap
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
